Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
updates
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

\section{Services Built on
Malacology}\label{services-built-on-malacology}

\label{services}

\begin{table}
\begin{tabular}{ | l | l | l | l | l |}
\hline
Cap Owner & Failure & ZLog Recovery \\ \hline
mds & mds & mds \\ \hline
client & mds & xfer client cap \\ \hline
mds & client & n/a \\ \hline
client & client & mds \\
\hline
\end{tabular}
\caption{Failure and recovery scenarios.}
\label{t:mds-zlog-fail}
\end{table}

\subsection{Mantle: A Programmable Metadata Load
Balancer}\label{mantle-a-programmable-metadata-load-balancer}

@@

\subsection{ZLog Sequencer}

@@

@@

\subsubsection{Experiment: Multi-Client
Burstiness}\label{experiment-multi-client-burstiness}

\begin{figure}[htbp]
\centering
\includegraphics{figures/caps-delay-thruput.png}
\caption{Sequencer throughput by reusing various services.
The highest performance is achieved using a single client with
exclusive, cacheable priviledge. Round-robin sharing of the sequencer
resource is affected by the amount of time the resource is held,
with best-effort performing the worst.}
\label{fig:captp}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics{figures/caps-delay-latency.png}
\caption{But if the clients hold their capabilities longer, it hurts
latency for everyone.}
\label{fig:capcdf}
\end{figure}

@@

\subsubsection{CUT THIS Experiment: Client v. MDS caps +
Failures}\label{cut-this-experiment-client-v.-mds-caps-failures}

\subsubsection{Experiment: Mantle Sequencer
Balancer}\label{experiment-mantle-sequencer-balancer}

>>>>

\section{Services Built on Malacology}
\label{services}

In this section we describe two services built on top of Malacology. The first
is Mantle, a framework for dynamically specifying metadata load balancing
policies. The second system, ZLog, is a high-performance distributed shared-log.
In addition to these services, we'll demonstrate how we combine ZLog and Mantle
to implement service-aware metadata load balancing policies.

\subsection{Mantle: A Programmable Metadata Load Balancer}

@@

\subsection{ZLog}

@@

\begin{figure}[h]
\centering
\includegraphics{figures/caps-delay-thruput.png}
\caption{Sequencer throughput by reusing various services.
The highest performance is achieved using a single client with
exclusive, cacheable priviledge. Round-robin sharing of the sequencer
resource is affected by the amount of time the resource is held,
with best-effort performing the worst.}
\label{fig:captp}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics{figures/caps-delay-latency.png}
\caption{But if the clients hold their capabilities longer, it hurts
latency for everyone.}
\label{fig:capcdf}
\end{figure}

@@

\subsubsection{Interface Propogation}

@@
